Graph Exploration and Search

### 2017-11-14 exploratory.tex
minor
Corrected small bugs

%!TEX root=./paper.tex
\subsection{Exploratory Graph Analysis (Davide)}

\stitle{Example-based approaches}

@@

Examples have also been used as a mean to detect communities~\citep{staudt2014detecting,perozzi2014focused}, where a community is a set of nodes, in which every node is connected to many more nodes inside the community than outside. 
One approach is to consider each node in $v \in Q$ as a representative of a different community~\citep{staudt2014detecting}. 
In graphs with attributes on nodes, FocusCO~\citep{perozzi2014focused} introduced a clustering algorithm that learns a similarity function among nodes, based on the attributes in the examples.
Formally, FocusCO takes an attributed graph $G = (V,E,F)$, where $F$ is a feature matrix $F \in \mathbb{R}^n\times f$ and $F_{i\cdot}$ represents the attribute vector for node $v_i$, and returns cluster that better represent the seed nodes $Q$.
In addition, FocusCO returns outliers that do not belong to any community identified so far.

@@

\eetitle{Node tuples as examples.}
In Graph Query by Example (GQBE)~\citep{jayaram2015querying} a tuple of nodes $(v_1, ..., v_n), v_i \in V^n$ is a representative of the result tuples. 
For instance, if the pair (\emph{Yahoo, Jerry Yang}) is provided, the result is expectedly other \emph{IT company, founder} pairs. 
The solution first computes the \emph{minimal answer graph} connecting the query nodes and then finds other subgraphs isomorphic to the answer graph.

@@

\stitle{Reformulation of Graph Queries}

\noindent Users with exploratory intent typically provide indefinite queries that are likely to return either too few or too-many results. 
For this reason query reformulation techniques aim at modifying the query to lead the user to the intended result~\citep{mottin2015graph,hurtado2008query,islam2015efficient}. 
A \emph{reformulation} for a query $Q \subseteq G$ on a labeled graph $G = (V, E, \ell)$ with labeling function on nodes and edges $\ell$, is another query $Q'$ that is either a supergraph $Q' \subseteq Q$ or a subgraph $Q' \supseteq Q$ of $Q$. Therefore, $Q'$ can be more specific (supergraph) or more generic (subgraph) than $Q$. 
Queries considered in graph query reformulation are usually subgraph isomorphism queries~\cite{lee2012depth}.  
Query reformulation has been proposed for collections of graphs, or \emph{graph databases}, as well as \emph{large graphs}. 
%For simplicity the graph is considered unlabeled, even though the presented methods work mostly with labeled graphs. 
%the set of $\mathcal{R}(Q)=\{G' \subseteq G | G' \equiv Q \}$ with a

@@

Graph Query Reformulation (GQRef)~\citep{mottin2015graph} discovers query reformulations having small overlap and high coverage; thus ideally no result is missing from the reformulated queries, yet the reformulations have little redundancy. 
The objective is to find a set $R$ of $k$ reformulations with high coverage and diversity (i.e., small overlap)  maximizing $f(R) = |\bigcup_{Q \in R}\mathcal{R}(Q)|+ \lambda\sum_{Q_1,Q_2 \in R}|\mathcal{R}(Q_1) \cup \mathcal{R}(Q_2)|$. 
Maximizing $f$ is \NP-hard, but an approximate greedy solution can guarantee a $(1/2)$-approximation.

@@

Query reformulations are also used to debug queries and understand why the query returned too-many or too-few answers~\citep{vasilyeva2016answering}. 
In order to explain the dependency between the number of results and the query~\citep{vasilyeva2016answering} first computes the \emph{maximum common subgraph} (MCS) among the graph $G$ and the query $Q$, and then use a \emph{differential graph} to profile the query by adding edges from the differential graph to the MCS. 
The maximum common subgraph is the largest connected graph $G'$ that is subgraph of both $Q$ and $G$.

>>>>

%!TEX root=./paper.tex
\subsection{Exploratory Graph Analysis}

% \stitle{Example-based approaches}

@@

Examples have also been used as a mean to detect communities~\citep{staudt2014detecting,perozzi2014focused}, where a community is a set of nodes, in which every node is connected to many more nodes inside the community than outside. 
One approach is to consider each node $v \in Q$ as a representative of a different community~\citep{staudt2014detecting}. 
In graphs with attributes on nodes, FocusCO~\citep{perozzi2014focused} introduced a clustering algorithm that learns a similarity function among nodes, based on the attributes in the examples.
Formally, FocusCO takes an attributed graph $G = (V,E,F)$, where $F$ is a feature matrix $F \in \mathbb{R}^n\times f$ and $F_{i\cdot}$ represents the attribute vector for node $v_i$, and returns clusters that better represent the seed nodes $Q$.
In addition, FocusCO returns outliers that do not belong to any community identified so far.

@@

\eetitle{Node tuples as examples.}
In Graph Query by Example (GQBE)~\citep{jayaram2015querying} a tuple of nodes $(v_1, ..., v_n), v_i \in V^n$ is a representative of the result tuples. 
For instance, if the pair (\emph{Yahoo, Jerry Yang}) is provided, the result is expectedly other \emph{IT company, founder} pairs. 
The solution first computes the \emph{minimal answer graph} connecting the query nodes and then finds other subgraphs isomorphic to such graph.

@@

\subsection{Reformulation of Graph Queries}

\noindent Users with exploratory intent typically provide indefinite queries that are likely to return either too few or too-many results. 
For this reason query reformulation techniques aim at modifying the query to lead the user to the intended result~\citep{mottin2015graph,hurtado2008query,islam2015efficient}. 
A \emph{reformulation} for a query $Q \subseteq G$ on a labeled graph $G = (V, E, \ell)$ with labeling function on nodes and edges $\ell$, is another query $Q'$ that is either a supergraph $Q' \supseteq Q$ or a subgraph $Q' \subseteq Q$ of $Q$. Therefore, $Q'$ can be more specific (supergraph) or more generic (subgraph) than $Q$. 
Queries considered in graph query reformulation are usually subgraph isomorphism queries~\citep{lee2012depth}.  
Query reformulation has been proposed for collections of graphs, or \emph{graph databases}, as well as \emph{large graphs}. 
%For simplicity the graph is considered unlabeled, even though the presented methods work mostly with labeled graphs. 
%the set of $\mathcal{R}(Q)=\{G' \subseteq G | G' \equiv Q \}$ with a

@@

Graph Query Reformulation (GQRef)~\citep{mottin2015graph} discovers query reformulations having small overlap and high coverage; thus ideally no result is missing from the reformulated queries, yet the reformulations have little redundancy. 
The objective is to find a set $R$ of $k$ reformulations with high coverage and diversity (i.e., small overlap)  maximizing $f(R) = |\bigcup_{Q \in R}\mathcal{R}(Q)|+ \lambda\sum_{Q_1,Q_2 \in R}|\mathcal{R}(Q_1) \cup \mathcal{R}(Q_2)|$, with $\lambda$ trading-off coverage and diversity. 
Maximizing $f$ is \NP-hard, but an approximate greedy solution can guarantee a $(1/2)$-approximation.

@@

Query reformulation is also employed in query debugging to understand why the query returned too-many or too-few answers~\citep{vasilyeva2016answering}. 
In order to explain the dependency between the number of results and the query~\citep{vasilyeva2016answering} first computes the \emph{maximum common subgraph} (MCS) among the graph $G$ and the query $Q$, and then use a \emph{differential graph} to profile the query by adding edges from the differential graph to the MCS. 
The maximum common subgraph is the largest connected graph $G'$ that is subgraph of both $Q$ and $G$.
